---
title: "Data Wrangeling and Processing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{data_wrangling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(musicDemographicsPackage)
library(gdata)
library(dplyr)
library(tidyr)
library(ggplot2)
library(forcats)
library(cowplot)
library(viridis)
library(devtools)
```

## The code below reads in our data from the original excel files and transforms it into a usable tidy data set and exprots it to the data folder. This code also Modifys the variable names of the data sets to make them more usable for transformations and vizulizations.
```{r}
# Read and tidy data 1
# https://www.statista.com/statistics/253915/favorite-music-genres-in-the-us/
dt1 = read.xls("../inst/extdata/statistic_id253915_favorite-music-genres-in-the-us-2018-by-age.xlsx", sheet = 2, skip = 2,header = TRUE)
genres_by_age_2018 = rename(dt1, "genre" = "X","16-19" ="X16.19","20-24"="X20.24","25-34" ="X25.34","35-44" ="X35.44","45-54" ="X45.54","55-64" ="X55.64","65+" ="X65.") %>% 
select (-X.1)%>%
gather("age_range", "percent_response", -"genre")

# Read and tidy data 2
# https://www.statista.com/statistics/749666/music-listening-habits-age-usa/
dt2 = read.xls("../inst/extdata/statistic_id749666_music-listening-frequency-in-the-us-2017-by-age.xlsx", sheet = 2,  skip = 2,header = TRUE)
listening_frequency_by_age_2017 = rename(dt2, "Generation" = "X","4-6 per week" ="X4.6.times.a.week","1-3 per week"="X1.3.times.a.week","Few Times a Month" ="Few.times.a.month","Monthly or Less" ="Monthly.or.less") %>% select (-X.1) %>% gather("Frequency", "percent", 2:7)

# Read and tidy data 3
# https://www.statista.com/statistics/864622/music-genre-diversity/
dt3 = read.xls("../inst/extdata/statistic_id864622_music-genres-which-have-the-most-racial-diversity-in-the-us-2018.xlsx", sheet = 2, skip = 2, header = TRUE)
racially_diverse_music_2018 = rename(dt3, "genre" = "X","percent_response" ="Share.of.respondents") %>% select (-X.1)

# Export Data Sets
use_data(genres_by_age_2018, overwrite = TRUE)
use_data(listening_frequency_by_age_2017, overwrite = TRUE)
use_data(racially_diverse_music_2018, overwrite = TRUE)
```

## This code segment combinds the data from data set 1 and the data from data set 2 and creates a new tidy data set from them that describes peoples preference for music genres as well as how people feel about how diverse a genre is.
```{r}
# https://www.statista.com/statistics/864622/music-genre-diversity/
dt3 = read.xls("../inst/extdata/statistic_id864622_music-genres-which-have-the-most-racial-diversity-in-the-us-2018.xlsx", sheet = 2, skip = 2, header = TRUE)
# Rename  the columns so that we can join the data
racially_diverse_music_2018_2 = rename(dt3, "genre_old" = "X","diverse_percent_response" ="Share.of.respondents") %>% select (-X.1)

# Change the values of the genres so that they match the ones in genres_by_age_2018
racially_diverse_music_2018_mod <- racially_diverse_music_2018_2 %>% 
mutate(genre = case_when(
        genre_old == "Rap/Hip-Hop" ~ "Hip Hop/Rap",
        genre_old == "Pop" ~ "Pop Music",
        genre_old == "Jazz" ~ "RnB (Rhythm and Blues)",
        genre_old == "Blues" ~ "RnB (Rhythm and Blues)",
        genre_old == "R&B" ~ "RnB (Rhythm and Blues)",
        genre_old == "Reggae" ~ "RnB (Rhythm and Blues)",
        genre_old == "Classic rock" ~ "Classic Rock",
        genre_old == "World Music" ~ "Indie/Alternative Rock",
        genre_old == "Soul/Funk" ~ "RnB (Rhythm and Blues)",
        genre_old == "Alternative/Indie" ~ "Indie/Alternative Rock",
        genre_old == "Dance/Electronic" ~ "Instrumental",
        genre_old == "Hard rock/Metal" ~ "Rock Music",
        genre_old == "Punk Rock" ~ "Rock Music",
        genre_old == "Country" ~ "Country/Western",
        genre_old == "Contemporary Christian" ~ "Indie/Alternative Rock",
        genre_old == "New Age" ~ "Indie/Alternative Rock",
        genre_old == "Classical" ~ "Instrumental",
        genre_old == "Folk" ~ "Indie/Alternative Rock"))

# remove the unused column
racially_diverse_music_2018_mod <- racially_diverse_music_2018_mod %>% select (-genre_old)

# remoe NA
racially_diverse_music_2018_mod <- drop_na(racially_diverse_music_2018_mod)

#avg same genres
racially_diverse_music_2018_mod <- racially_diverse_music_2018_mod  %>% group_by(genre) %>% summarise(avg_response = mean(diverse_percent_response)) 

# combninde the data in racially_diverse_music_2018_mod and genres_by_age_2018 by joining on genre
combined_data <- racially_diverse_music_2018_mod %>% inner_join(genres_by_age_2018, by = "genre")

# Re order data columns and asign new data set
liked_diverse_music_combo <- rename(combined_data[c(2,3,1,4)], "likeability_percent_response" = "percent_response")

# export data
use_data(liked_diverse_music_combo, overwrite = TRUE)
use_data(racially_diverse_music_2018_mod, overwrite = TRUE)
```

